The problem and promise of scale in multilayer networks

### 2019-09-12 paper/introduction.Rmd
more box 1

# Introduction

Animal social systems are complex and multifaceted

@@

# Box 1: Types of spatiotemporally explicit data

Spatial data can be:

>>>>

# Introduction
Animal social systems are complex and multifaceted

@@

# Box 1: Types of spatial variables 
Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers. Edges connect different entities in the same layer or across layers as well as to the same entities across layers. The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within. Depending on the type, a multilayer network may include one or both of these types of spatial variables to better understand the complex connections between social systems and the landscapes they

The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and *landscape scale data. * Georeferenced biologging data, including radio-frequency identification tags, radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to time and labour intensive direct observations of individuals and their interactions [@krause2011]

Land cover, land use

Edges between nodes can define individual's associations, preda
